Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-06-11 LaTeX_paper/paper.tex
paper backup

@@

% figure of a mesurement error
\begin{figure}[h]
    \caption{An example of what can go wrong when dealing with the real world}\label{fig:figure_measurement_error}
    \includegraphics[height=0.25\textwidth]{pictures/example_bad_piece.jpg}
    \centering

@@

\subsection{Computer Vision Powers Automatic Jigsaw Puzzle Solver~\cite{Abto}}
The solutions~\ref{document:GCL} and~\ref{document:GA} can be considered “state of the art” for digital jigsaw puzzles.
But, as already introduced in section~\ref{document:DigitalVSReal} and better explained in section TODO,
appalling the solution to the real world can be challenging.\newline
This solution is possibly a “state of the art” for real world puzzles.\newline
In reality calling this a “solution” is incorrect,
since all it does is find the best 8 matches and asks the user which one to place.
Making the algorithm not autonomous.\newline
Even ignoring this major detail, making an analysis of this solution has proven to be challenging,
since the article is more of a publicity stunt than an academic paper.
In fact, the code is not open source and the information about the time needed to solve the puzzle is missing.\newline
The article only shows a single puzzle solved, with a 9x6 dimension.\newline
Even with all of these problems this article still is one of the best example of a solution for real world puzzle.

\section{The objective of this paper}
After reading some of the previous literature for this problem, some conclusions could be drawn:
The problem of “digital jigsaw puzzle” has been solved many times, and is already well optimized.\newline
On the other hand, the problem of “real world jigsaw puzzle” has mostly been ignored\newline
by the academic community.\newline

@@

@@

  %Graph Connection Laplacian
  \bibitem{GCL}
    Vahan Huroyan, Gilad   Lerman and Hau-Tieng Wu,
    Solving Jigsaw Puzzles By The Graph Connection Laplacian,
    2020.
    \url{https://arxiv.org/pdf/1811.03188.pdf}.

  % Genetic algorighm
  \bibitem{GA}
    Dror Sholomon, Omid David and Nathan S. Netanyahu,
    A Genetic Algorithm-Based Solver for Very Large Jigsaw Puzzles,
    2013.
    \url{https://openaccess.thecvf.com/content_cvpr_2013/papers/Sholomon_A_Genetic_Algorithm-Based_2013_CVPR_paper.pdf}.

>>>>

% for sub figures
\usepackage{subcaption}

@@

% figure of a mesurement error
\begin{figure}[h]
    \caption{An example of what can go wrong when dealing with the real world}\label{fig:figure_measurement_error}
    \includegraphics[height=0.25\textwidth]{pictures/example_bad_piece.jpg}
    \centering
\end{figure}

@@

\subsection{Computer Vision Powers Automatic Jigsaw Puzzle Solver~\cite{Abto}}
The solutions~\ref{document:GCL} and~\ref{document:GA} can be considered “state of the art” for digital jigsaw puzzles.
But, as already introduced in section~\ref{document:DigitalVSReal} and better explained in section TODO,
appalling the solution to the real world can be challenging.\newline
This solution is possibly a “state of the art” for real world puzzles.\newline
In reality calling this a “solution” is incorrect,
since all it does is find the best 8 matches and asks the user which one to place.
Making the algorithm not autonomous.\newline
Even ignoring this major detail, making an analysis of this solution has proven to be challenging,
since the article is more of a publicity stunt than an academic paper.
In fact, the code is not open source and the information about the time needed to solve the puzzle is missing.\newline
The article only shows a single puzzle solved, with a 9$\times$6 dimension.\newline
Even with all of these problems this article still is one of the best example of a solution for real world puzzle.

\section{The Objective Of This Paper}
After reading some of the previous literature for this problem, some conclusions could be drawn:
The problem of “digital jigsaw puzzle” has been solved many times, and is already well optimized.\newline
On the other hand, the problem of “real world jigsaw puzzle” has mostly been ignored\newline
by the academic community.\newline

@@

\section{The Setup}

To answer these questions, some data to start with,
and an algorithm to analyze the data; in particular the necessary components are:

\subsection{The Puzzle To Solve}

The first step is finding a real world puzzle to solve;
It has been decided to use a classic 500 piece puzzle, and use a printer's
scanner to digitize the pieces.\newline
The puzzle has been scanned in various sub-sizes to allow the testing of different configurations. 
A resolution of 1200 ppi has been used to ensure a sharp and precise image
of the piece, as seen in image~\ref{fig:figure_measurement_error}.
The puzzle has been scanned backward, since the comparator algorithm
that has been used REF does not use colors,
and having an uniform color would make splitting the pieces easier.

\subsection{Splitting The Pieces}
As introduced in section~\ref{document:splitter}, the first step to solve a puzzle
is to split an image composed of many pieces into individual ones.
This is relatively straightforward, and can be done with the following steps:

\begin{itemize}
  \item Apply a threshold and transform an RGB image into a binary mask.
  \item Find all individual Blobs
  (a Blob is just set of connected pixels with the same color) and for each one:

  \begin{itemize}
  \item Calculate the area (the number of pixels the Blob is made of)

  \item Add it to the set of pieces only if his area in within a certain range (to avoid small pieces of dust ending up counted as pieces)

\subsection{Splitting The Sides}

The next step following the general template~\ref{document:splitter}
is to split a pieces into
his 4 sides, this could be done with the following steps:

\begin{itemize}

  \item \textbf{Remove the holes from the piece:}\newline
  To do so the program computes the convex hull of the piece,
  then calculates the difference between the convex hull and the original image,
  and obtains an image with the “filler areas”.
  These filler areas have very different shapes,
  depending on what has generated them (a “hole” or a “knob” in the piece).
  So they can be classified, and added to the original piece only if
  they are generated by a hole, obtaining an image without holes.

  \item \textbf{Remove the knobs from he piece}\newline
  To do so the image without holes gets eroded and then dilated.
  This generates an image that resembles the original one, but has no knobs.
  Then the program finds the pixels that are white in the image without holes,
  but not in the image that has been eroded and dilated. This generates a set of Blobs,
  but again, the shape of the blob is very different depending on what has generated it
  (an “angle” or a “knob”), so they can be classified.
  Then the program removes from the image with no holes all the pixels that are
  close to a Blob generated by a knob, obtaining an image without knobs and holes.

\begin{figure}
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{pictures/remove_holes_convex_hull.png}
    \caption{Caption for Image 1}
    \label{fig:image1}
  \end{subfigure}
  \begin{subfigure}{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{pictures/remove_holes_convex_hull.png}
    \caption{Caption for Image 2}
    \label{fig:image2}
  \end{subfigure}
  \caption{Overall caption for the figure}
  \label{fig:overall}
\end{figure}

@@

  %Graph Connection Laplacian
  \bibitem{GCL}
    Vahan Huroyan, Gilad   Lerman and Hau-Tieng Wu,
    Solving Jigsaw Puzzles By The Graph Connection Laplacian,
    2020.
    \url{https://arxiv.org/pdf/1811.03188.pdf}.
  % Genetic algorighm
  \bibitem{GA}
    Dror Sholomon, Omid David and Nathan S. Netanyahu,
    A Genetic Algorithm-Based Solver for Very Large Jigsaw Puzzles,
    2013.
    \url{https://openaccess.thecvf.com/content_cvpr_2013/papers/Sholomon_A_Genetic_Algorithm-Based_2013_CVPR_paper.pdf}.
